Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2021-06-21 docs/00-manuscripts/ieee/ieee-manuscript.tex
clarify percentage values in table VII

The large differences of selected features per fold during tuning give interesting insights into internals of the used models (\autoref{tab:tune-perc-sel-features}).
While in most cases, SVM and XGBoost require a substantial portion of all available features to achieve robust predictions, RF was able to achieve the best results with a relatively small amount of features.
Realizing early that few features are needed during tuning to reach adequate performances can reduce the overall computational runtime substantially, especially when iterating over parameters such as $m_\textrm{try}$ whose optimum (and range) depends on the number of features.
Hence, regardless of the potential advantage of using filters for increased predictive performance, it should be noted that these can have a strong positive effect on runtime, at least for RF in this study.

>>>>

The large differences of selected features per fold during tuning give interesting insights into internals of the used models (\autoref{tab:tune-perc-sel-features}).
Values of selected feature percentages like 99.97268 \% in \autoref{tab:tune-perc-sel-features} emerge from the specific setting which got elected as the best setting during the tuning step.
The value for the amount of features to select is initially defined by an internal surrogate learner of the MBO tuning method and can be any numeric value between 0 and 1.

While in most cases, SVM and XGBoost require a substantial portion of all available features to achieve robust predictions, RF was able to achieve the best results with a relatively small amount of features.
Realizing early that few features are needed during tuning to reach adequate performances can reduce the overall computational runtime substantially, especially when iterating over parameters such as $m_\textrm{try}$ whose optimum (and range) depends on the number of features.
Hence, regardless of the potential advantage of using filters for increased predictive performance, it should be noted that these can have a strong positive effect on runtime, at least for RF in this study.
